Training a Gaming Agent on Brainwaves

### 2020-10-12 review2/response.letter.tex

\subsection*{\ovalbox{Reviewer 1 General Comments}}

Comments to the Author
The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

Training a Gaming Agent on Brainwaves
The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
Page 1
The abstract still reads like an introduction until the last sentence.  I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”

\begin{quotation}
{\color{blue}
We started the abstract as suggested, thank you very much for it.  We rewrote the abstract detailing the obtained results.
}
\end{quotation}

@@

Expand the results of the paper as this is the contribution.
“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
Both the underlined terms need to cite evidence from the paper.

\begin{quotation}
{\color{blue}
We included this information in the abstract and added it in the Conclusions Section (IV).
}
\end{quotation}

@@

Line 40 “This information is used to make a gaming agent $<$that$>$ improves ....”

\begin{quotation}
{\color{blue}
This text is no longer contained in the manuscript.  We verified along the Manuscript to avoid similar mistakes.
}
\end{quotation}

@@

Line 11 col 2 “how biological agents learn from its $<$their$>$ environment by exploring it and getting feedback rewards, either negative or positive.”

\begin{quotation}
{\color{blue}
This text is no longer contained in the manuscript.  We verified along the Manuscript to avoid similar mistakes.
}
\end{quotation}

Line 17 col2 "\sout{Nonneglected} is the influence of DeepBrain’s AlphaGo project,” // Re-word

\begin{quotation}
{\color{blue}
This was already solved in a previous version, and the manuscript no longer contains this line.  We appreciate a lot for your suggestion.
}
\end{quotation}

@@

Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)

\begin{quotation}
{\color{blue}
We added the missing information on Section II.A.  Thanks for pointing out this important issue.
}
\end{quotation}

Page 2
Line 56 “Data \sout{is} $<$are$>$ handled and processed with the OpenVibe Designer,” // datum-data

\begin{quotation}
{\color{blue}
Fixed issue for every appearances of \textbf{data is}.
}
\end{quotation}

@@

Page 4
Lin 24 This allows \sout{to learn} the Q-Table $<$to learn$>$ based on the subject’s feedback from the movements the agent
took, which are chosen pseudo-randomly, while executing the brainwave session.

\begin{quotation}
{\color{blue}
Fixed issue.  We appreciate a lot the level of detail in the comments.
}
\end{quotation}

Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion. Is a best performance of 0.672 useful/acceptable? How does it compare to other researchers (if a comparison is possible).

\begin{quotation}
{\color{blue}
On Section IV, third paragraph we tackled this issue.  The overall performance of 0.672 is low.  Although a comparison can be misleading in the context of the ErrP experiment, we added a brief comparison to other similar works.  We also emphasized this point in future works where there is room for improvement in terms of the classification and processing pipeline.
}
\end{quotation}

@@

Line 42 col 2 “These results are also consistent with their classification ROC curves, shown \sout{on} $<$in$>$ Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one. This would provide the basis for comparison.

\begin{quotation}
{\color{blue}
We emphasize on the Figure 6 caption which ROC curves where good which were not so good.  We added this in the text and the important finding that we could not provide an enhencement of the agent for those subjects where the obtained ROC curves were not good.
}
\end{quotation}

@@

Page 5
Figure 5 “Y axis shows the averaged number of steps, while x axis show the number of
experiences used to cumulative train the Q-Table.”
// Why does Fig5 E only have 2 sets of data? Some discussion of the (smaller) change from 1 – 2 would be appropriate (e.g. I Discussion)
Line 51 “No\sout{t} performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value

\begin{quotation}
{\color{blue}
We fixed the inappropriate wording, and appreciate the Reviewer for pointing this out.  
Figure 5, for Subject 5 (in the first version of the manuscript it was labeled E) has only two sets of data because that Participant (OHC) couldn't complete more sessions.  Hence we used two training sessions to calculate the Q-Table and subsequently performed the run session (i.e. the agent performs movements randomly based on the trained QTable for 200 iterations).
}
\end{quotation}

@@

Line 55 “It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.” // more explanation/discussion needed. Is this an average effect from positive learners?

\begin{quotation}
{\color{blue}
This is a great question.  Traditional Transfer Learning strategies focus on the procedure to enrich a classifier training it with a vast dataset and using it to generalize to new data or unseen scenarios.  While deaing with EEG data, this strategy tends to fail, and other approaches are required.  We found in this work, that even when that strategy fails, if the system is coupled with a basic reinforcement learning algorithm, the cumulative rewards from different subjects, can be used to effectively transmit information and improve the agent performance.  We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity it will lead to eventually learn, and the usage of various OHCs help to increase the available data to do so.
}
\end{quotation}

@@

This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning. The collected data show that ErrP signals can in fact be classified and used to train an agent effectively. // Can you link these findings to confirm/challenge other recent research in Err potentials

\begin{quotation}
{\color{blue}
We believe this result is quite supported in the literature.  You can check here here here here here.  Our novel approach is to use the rewards to train an agent that can perform on its own after the training has been performed, and the game mechanics to verify the flow of information.  This information was added in the Conclusion Section IV.
}
\end{quotation}

@@

Page 6
Fig 8 – why use data from subject 6 (a non-learner)?

\begin{quotation}
{\color{blue}
Subject 5 and 6 aren't used to train the algorithm in this instance. This information was emphasized on the Figure's caption and on the main text in the Result Section.
}
\end{quotation}

@@

Line 42 “However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning” //

Line 20 col 2 Despite that, the rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
//These are key findings, worth more discussion/interpretation and inclusion in abstract.

\begin{quotation}
{\color{blue}
We added it because is a very interesting results to overcome issues in transfer learning while dealing with biological data.  We appreciate the reviewer for this very important point.
}
\end{quotation}

### 2020-10-12 ErrP.tex
Completé la respuesta a casi todas las preguntas, modifiqué el texto en concordancia.  Hice unos cambios para enfatizar que la contribución es la mecánica y el agente del juego.

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.  The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.

@@

\label{cognitive_experiment_system}{
The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.  A blue spot indicates the current position of the agent and a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}. The agent's objective is to reach the goal. The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent starts at the upper-left position of the grid and moves in each iteration.  When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the match has ended. There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and the right, and those movements are bounded to avoid the agent from leaving the grid. The movement direction is selected randomly and is executed once every 2 seconds.  After each gameplay, there is a pause of 5 seconds until the next match starts. Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.  This is considered a stimulus to the observational human critic.  The game is designed as to be evident whenever there is an error (i.e. the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.6\textwidth]{revisedimages/avg_closer.eps}
    \includegraphics[width=0.6\textwidth]{revisedimages/avg_further.eps}
    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
    \label{fig:classifiers}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
    \includegraphics[height=40pt,width=1.20\textwidth]{revisedimages/avg_5_segments.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

@@

Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.  This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC and a classifier that was trained using the brainwaves from a different Trainer OHC.  The figure shows the cumulative variation for all run sessions on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.  Enhancements are shown as negative values.  Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.  For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.

@@

This work aims to propose a simple game that can use the ErrP component to train a gaming agent using a RL model. The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.

@@

One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.

The obtained accuracy to discriminate ErrPs is low, similar results were obtained in  \cite{Ehrlich2016}.

However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.  Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity. On the other hand, the percentage of false negatives is generally higher.  However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning. Though scarce, accurate rewards are very useful for the RL algorithm.
%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.

>>>>

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.   The game is similar to this one \cite{Iturrate2013}.

Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.  The three contributions are (1) a simple game mechanics and agent that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low but with a high specificity and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.

%However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning

@@

\label{cognitive_experiment_system}{
The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.  It is similar to the one proposed by~\cite{Iturrate2013}.  A blue spot indicates the current position of the agent and a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}. The agent's objective is to reach the goal. The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent starts at the upper-left position of the grid and moves in each iteration.  When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the match has ended. There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and the right, and those movements are bounded to avoid the agent from leaving the grid. The movement direction is selected randomly and is executed once every 2 seconds.  After each gameplay, there is a pause of 5 seconds until the next match starts. Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.  This is considered a stimulus to the observational human critic.  The game is designed as to be evident whenever there is an error (i.e. the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_closer.eps}
    \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
    \label{fig:classifiers}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
    \includegraphics[scale=0.21]{revisedimages/avg_5_segments.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

@@

Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.  This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC and a classifier that was trained using the brainwaves from a different Trainer OHC.  The figure shows the cumulative variation for all run sessions on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.  Enhancements are shown as negative values.  Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.  For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information provides no value.

@@

This work aims to propose a simple game mechanics that can use the ErrP component to train a gaming agent using a RL model. The collected data and the shows that ErrP signals can in fact be classified and used to train an agent effectively.

@@

One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.   The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.  In this regard, dispite of the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\% of accuracy are reported~\cite{Chavarriaga2014}.  However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.  Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity. On the other hand, the percentage of false negatives is generally higher.  However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning. Though scarce, accurate rewards are very useful for the RL algorithm.
%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
